Spin canonical divisors of log stacky curves

### 2015-06-19 stacky_write_up/spin_cring.tex
paste saturation list, add temporary table of cts

@@

\subsection{Main Results}
These are our results.
\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature
$\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,\halfcan)$ is
generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with
relations in degree at most $2e$, so long as $\sigma$ does not lie
in a finite list of exceptions. \todo{Rewrite this to be more
precise}
\end{thm}
\begin{proof}

@@

@@

\item The elements $y_{e-2}^ay_e^b,$ with $a \geq 0, b > 0$ span $R$
			over $R'$ and the element $y_e$ minimally generates $R$ over $R'$.
\item Equip $k[y]$ and $k[x]$ with any graded monomial order and
			$k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I.$
			Then,
			\begin{align*}
					in_\prec(I) = in_\prec(I')k[x,y] + \langle y_ez \mid z \neq y_e,y_
					{e-2} \rangle 
			\end{align*}
			as $z$ ranges over generators of $R$.
\item Suppose $in_\prec(I')$ is minimally generated by quadratics 
				and that $e > \deg z$ for any generator $z$ of $R'.$ Then any set 
				of minimal generators for $I'$ together with any set of relations 
				as in the previous part \todo{reference previous part as part c} 
				minimally generate $I$. \todo{prove this still}
\item $(\sx,e)$ is admissible.
\end{enumerate}
\end{thm}

>>>>

\tableofcontents

@@

\subsection{Main Results}
These are our results.
\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx,\halfcan)$ is a spin curve, so that $\sx$ has signature
$\sigma = (0;e_1,\ldots, e_r;0)$, then $R(\sx,\halfcan)$ is
generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with
relations in degree at most $2e$, so long as $\sigma$ does not lie
in a finite list of exceptions. \todo{Rewrite this to be more
precise}
\end{thm}

@@

Here we compute saturation numbers. That is, given a list of
ramification orders, with $g = 0,\delta = 0$ understood, we have
the following saturations of the canonical divisor, as defined in
7.2 of Voight and Zureick-Brown \cite{vzb:stacky}
\begin{enumerate}
	\item $(3,3,3)$ exceptional, we know it it is $k[x]$ in degree 3.
	\item $(3,3,5) \mapsto 18.$ (gen in 3, 10, 15; min relations in 30)
	\item $(3,3,7) \mapsto 12.$ (gen in 3, 7, 12; min relation in 24) 
	\item $(3,3,9) \mapsto 12.$ (gen in 3, 7, 9; min relation in 21)
	\item $(3,3,k) \mapsto 9$ for $k > 9$. (gen in 3, 7, ..., $k$; 
min relation in 14 up to $2(k-1)$)
	\item $(3,5,5) \mapsto 8.$ (gen in degree 3, 5, 10; min relation 
in 20)
	\item $(5,5,5)\mapsto 8$ (gen in degree 3, 5, 5; min relation in 
15)
	\item $(a,b,c)\mapsto 5$ if $a,b,c$ is not listed above. (
generation in 3,5,7.) ($(a,b,c) = (3,5,7)$ generated in degree 3,5,7
, some relation in degree 30, might be more).
	\item $(3,3,3,3) \mapsto 6$ (monoid generation in degree 3,4) (
the actual ring is also generated in degree 4 with 1 relation in 
degree 12).
	\item If $(e_1,\ldots, e_r)$ is not listed above it has 
saturation $3$. (generation in 3,4,5.)
\end{enumerate}
\todo{make table and put proof}

@@

\item The elements $y_{e-2}^ay_e^b,$ with $a \geq 0, b > 0$ span $R$
		over $R'$ and the element $y_e$ minimally generates $R$ over $R'$.
\item Equip $k[y]$ and $k[x]$ with any graded monomial order and
		$k[y,x] = k[y] \otimes k[x]$ with block order. Let $R = k[y,x]/I$.
		Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_ez \mid z \neq y_e,y_
			{e-2} \rangle 
		\end{align*}
		as $z$ ranges over generators of $R$.
\item Suppose $in_\prec(I')$ is minimally generated by quadratics 
		and that $e > \deg z$ for any generator $z$ of $R'.$ Then any set 
		of minimal generators for $I'$ together with any set of relations 
		as in the previous part \todo{reference previous part as part c} 
		minimally generate $I$. \todo{prove this still}
\item $(\sx,e)$ is admissible.
\end{enumerate}
\end{thm}
